---
title: "Toronto AirBnB listing Analysis"
author: "YOUNG JUN JEONG"
date: "18/JULY/2021"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---
## PART 1: Non-spatial descriptive statistics

#### Installing packages

```{r, message=FALSE, warning=FALSE}
# install.packages("rtools")
# install.packages("tidyverse")
# install.packages("sf")
# install.packages("lwgeom")
# install.packages("mapboxapi")
# install.packages("leaflet")
# install.packages("reshape2")
# install.packages("geojsonio")
```

#### Loading libraries

```{r, message=FALSE, warning=FALSE}
library("tidyverse")
library("sf")
library("lwgeom")
library("mapboxapi")
library("leaflet")
library("reshape2")
library("geojsonio")
```

#### Importing non-spatial data

```{r, message=FALSE, warning=FALSE}
listings <- read_csv("toronto-listings.csv")
```
------------------------------------------------------------------------

```{r, message=FALSE, warning=FALSE}
listings$price <- substring(listings$price, 2, nchar(listings$price)-3) # 1
listings$price <- as.numeric(listings$price) # 2

listings <- listings %>% # 3
  mutate(bathrooms = as.numeric(str_split_fixed(listings$bathrooms_text, " b", 2)[,1])) %>% # 4
  filter(!is.na(room_type) & room_type == "Entire home/apt") # 5

```


1.  Changed data in price column to have only integer part by substring
    function
2.  Changed listings\$price from character type to numemric type
3.  Piping and applying the following functions to listings list
4.  Created bathroom column which has character before ' b' in numeric
    type
5.  Retrieve only columns that room_type is not NA or equals to 'Entire
    home/apt'

------------------------------------------------------------------------

```{r}
neighbourhood_cleansed_df <- listings %>%
  group_by(neighbourhood_cleansed) %>%
  summarise(neighbourhood_cleansed_n = n()) %>%
  filter(neighbourhood_cleansed_n == max(neighbourhood_cleansed_n))

name_neighbourhood_cleansed <- as.character(neighbourhood_cleansed_df[,1])
count_neighbourhood_cleansed <- as.numeric(neighbourhood_cleansed_df[,2])
```
The most frequent neighbourhood where Airbnbs are
located is **`r name_neighbourhood_cleansed `** with
**`r count_neighbourhood_cleansed`** Airbnbs.

------------------------------------------------------------------------
Some Airbnbs require you to rent the space for 2 or more nights. 
total_cost variable represents the minimum amount of money needed to rent the Airbnb. Additionally, NA values are removed from the total_cost column

```{r}
listings <- listings %>%
  filter(!(is.na(minimum_nights) | is.na(price))) %>%
  mutate(total_cost = price * minimum_nights)
```
------------------------------------------------------------------------

The mean and the median total cost of Airbnbs in
Toronto with the following criteria:
1.  Minimum number of nights is equal to or less than 3
2.  Number of bathrooms is equal to two or more

```{r}
mean_med_total_cost <- listings %>%
  filter(minimum_nights <= 3 & bathrooms >= 2) %>%
  summarise(mean_total_cost= mean(total_cost),
            median_total_cost = median(total_cost)) %>%
  round(digits = 1)
mean_total_cost <- as.numeric(mean_med_total_cost[,1])
median_total_cost <- as.numeric(mean_med_total_cost[,2])
```

The average cost of an Airbnb in Toronto with a
minimum of 3 or fewer nights is **`r mean_total_cost`** and the median
cost is **`r median_total_cost`**. Also, the distribution of total cost of an Airbnb in Toronto is right-skewed since mean is larger than median.
------------------------------------------------------------------------

```{r}
iqr_total_cost <- listings %>%
  filter(minimum_nights == 1) %>%
  summarise(q1_total_cost = quantile(total_cost, 0.25),
            q3_total_cost = quantile(total_cost, 0.75)) %>%
  mutate(iqr_total_cost = q3_total_cost - q1_total_cost)

```

The interquartile range of total cost for one-night
minimum Airbnbs in Toronto is **`r iqr_total_cost[1]` to
`r iqr_total_cost[2]`**.

------------------------------------------------------------------------

A boxplot  of the total cost of Airbnbs that
require minimum of 1 night only.

```{r}
listings %>%
  filter(minimum_nights == 1) %>%
  ggplot(aes(x = 0, y = total_cost)) +
  geom_boxplot() +
  ylab('Total Cost')
```


The IQR is defined as the range of middle-half (50%)
of the total cost data is **`r iqr_total_cost[3]`**. 
The boxplot tells that the data is extremely right-skewed.

------------------------------------------------------------------------

## PART 2: Spatial descriptive statistics

#### Importing data

```{r, message=FALSE, warning=FALSE}
# IMPORT AND CONVERT DATA
ls <- st_as_sf(listings, coords = c("longitude", "latitude"), crs = 4326) # Toronto Airbnb listings, ls = listings spatial
ls <- st_transform(ls, crs = 32617)

nbs <- st_read("toronto-neighbourhoods.geojson", crs = 4326) # Toronto neighbourhoods, nb = neighbourhoods
nbs <- st_transform(nbs, crs = 32617)
nbs_sp <- geojson_read("toronto-neighbourhoods.geojson", what = "sp") # Used for mapping

poi <- st_read("Places-of-Interest-and-Attractions.geojson") # Points of Interest in Toronto, poi = Points of Interest

poi_m <- st_transform(poi, crs = 32617) # poi_m = Points of Interest in meters

# CREATE LAT/LON COLUMNS
ls$coords <- as.character(ls$geometry)
ls$coords <- substring(ls$coords, 3, nchar(ls$coords)-1)
ls <- ls %>%
  mutate(longitude_m = as.numeric(str_split_fixed(ls$coords, ", ", 2)[,1]),
         latitude_m = as.numeric(str_split_fixed(ls$coords, ", ", 2)[,2]))

poi$coords <- as.character(poi$geometry)
poi$coords <- substring(poi$coords, 3, nchar(poi$coords)-1)
poi <- poi %>%
  mutate(longitude = as.numeric(str_split_fixed(poi$coords, ", ", 2)[,1]),
         latitude = as.numeric(str_split_fixed(poi$coords, ", ", 2)[,2]))

poi_m$coords <- as.character(poi_m$geometry)
poi_m$coords <- substring(poi_m$coords, 3, nchar(poi_m$coords)-1)
poi_m <- poi_m %>%
  mutate(longitude_m = as.numeric(str_split_fixed(poi_m$coords, ", ", 2)[,1]),
         latitude_m = as.numeric(str_split_fixed(poi_m$coords, ", ", 2)[,2]))


nbs$coords <- as.character(nbs$geometry)
nbs$coords <- substring(nbs$coords, 3, nchar(nbs$coords)-1)
nbs <- nbs %>%
  mutate(longitude = as.numeric(str_split_fixed(nbs$coords, ", ", 2)[,1]),
         latitude = as.numeric(str_split_fixed(nbs$coords, ", ", 2)[,2]))
```

------------------------------------------------------------------------
#### Creating example criteria of a customer
Creating a new dataframe considering an example criteria of:
  - 5 customers would like to rent an Airbnb in Toronto for 5 nights
  - The customers are planning to spend some time in the city and visit Toronto's museums
  - No more than \$250/night (collectively)
  - Minimum 2 bathrooms
  - Airbnb must accommodate 5 or more people.



```{r, message=FALSE, warning=FALSE}
criteria_ls <- listings %>%
  filter(minimum_nights <= 5 &
      price <= 250 &
      bathrooms >= 2 &
      accommodates >= 5)
```

------------------------------------------------------------------------

You and your 4 friends would also like to stay in a neighbourhood that
is in the middle of art gallery locations in the city, so you are
located centrally.

1.  Filter the Points of interest ('poi') dataframe to select only Art
    Galleries ('Gallery')
2.  Create 3 map icon/markers for the map. Be creative with your
    icon/marker image, but make sure it is representative and the
    resulting map is clear.
3.  Create the leaflet map with:

-   A basemap (your choice)

-   An appropriate zoom level

-   Map markers

    -   Airbnbs
    -   Art galleries with a popup with the gallery name
    -   Mean centre of art galleries
    -   Neighbourhoods with a popup with the neighbourhood name

4.  Identify the neighbourhood where the mean centre of art galleries is
    located.
5.  Identify the lowest cost Airbnb within the identified neighbourhood.
6.  Write a sentence identifying the following with inline code:

-   Cheapest cost Airbnb within neighbourhood
-   Cost of the Airbnb for a five-night stay
-   A clickable URL link ('listing_url') to the Airbnb you will stay

```{r}
# 1. Filtering the points of interest
poi <- poi %>%
  filter(CATEGORY == 'Gallery')
```


```{r}
# 2. Creating point markers to map the points

# Airbnbs
customPoint <- makeIcon(
  iconUrl = "https://cdn.discordapp.com/attachments/771483303093600316/864514198809870356/wfwef.png",
  iconWidth = 25, iconHeight = 25,
  iconAnchorX = 12.5, iconAnchorY = 12.5
)

# Art galleries
artgallery_pts <- makeIcon(
  iconUrl = "https://commonculture.org.uk/wp-content/uploads/leaflet-maps-marker-icons/heritage.png",
  iconWidth = 30, iconHeight = 30,
  iconAnchorX = 15, iconAnchorY = 15
)


# Mean centre
mcIcon <- makeIcon(
  iconUrl = "https://cdn.discordapp.com/attachments/711692521566371960/967242819418877952/kisspng-google-maps-pin-bing-maps-mapquest-how-to-create-a-nice-map-pin-icon-in-photoshop-i-5b630ecb57b8e5.8437748615332185073593-removebg-preview.png",
  iconWidth = 40, iconHeight = 40,
  iconAnchorX = 20, iconAnchorY = 20
)

```


```{r}
# 3. Creating the leaflet map
leaflet() %>%
  
  # Adding map layer, basemaps http://leaflet-extras.github.io/leaflet-providers/preview/index.html 
  addProviderTiles(providers$CartoDB.DarkMatter) %>%
  
  # Setting 1st view point (Map centre and zoom level)
  setView(lng = mean(criteria_ls$longitude),
          lat = mean(criteria_ls$latitude),
          zoom = 11.7) %>%
  
  # Airbnbs
  addMarkers(lng = criteria_ls$longitude,
             lat = criteria_ls$latitude,
             icon = customPoint,
             popup = paste(sep="<br/>",
                           paste(criteria_ls$name),
                           paste('Total cost: $',
                                 paste('<b>',criteria_ls$total_cost,'</b>')))) %>%
  
  
  # Art galleries
  addMarkers(lng = poi$longitude,
             lat = poi$latitude,
             icon = artgallery_pts,
             popup = paste(poi$NAME)) %>%
  
  # Mean centre
  addMarkers(lng = mean(poi$longitude),
             lat = mean(poi$latitude),
             icon = mcIcon,
             popup = paste('Mean Center')) %>%
  
  # Adding neighbourhoods
  
  addPolygons(data = nbs_sp,
              color='aquamarine',
              popup = paste('Neighbourhood:', nbs_sp$neighbourhood))



```


```{r}
# 4. Visualization based on the example criteria
mc_poi_neighbourhood <- 'Bay Street Corridor'


lowest_airbnb <- criteria_ls %>%
  filter(neighbourhood_cleansed == mc_poi_neighbourhood) %>%
  filter(total_cost == min(total_cost)) %>%
  select(name, total_cost, listing_url)

name_lowest_airbnb <- as.character(lowest_airbnb[,1])
cost_lowest_airbnb <- as.numeric(lowest_airbnb[,2])
listing_url <- as.character(lowest_airbnb[,3])
```

The cheapest cost Airbnb is named **`r name_lowest_airbnb`**
and it will cost **`r cost_lowest_airbnb`** dollars for the 5 night stay and the
[Airbnb can be seen here](`r listing_url`).

A neighbourhood is not a good method to search for an Airbnb
based on the mean centre of art galleries. As the leaflet map example shown above, it was a case that choosing a neighbourhood as a method for searching Airbnb becoming a problem due to Segmentation of Areal Units. The mean center was located very close to the borderline of one or two adjacent neighbourhood areas but 
realistically the calculation of minimum total cost of Airbnb is done within
the absolute boundary of the neighbourhood it locates.
------------------------------------------------------------------------
