---
title: "Assignment 1"
author: "YOUNG JUN JEONG"
date: "18/JULY/2021"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

# ASSIGNMENT 1: DESCRIPTIVE STATISTICS

## PART 1: Non-spatial descriptive statistics

#### OPTIONAL: INSTALL PACKAGES

```{r, message=FALSE, warning=FALSE}
# install.packages("rtools")
# install.packages("tidyverse")
# install.packages("sf")
# install.packages("lwgeom")
# install.packages("mapboxapi")
# install.packages("leaflet")
# install.packages("reshape2")
# install.packages("geojsonio")
```

#### LOAD LIBRARIES

```{r, message=FALSE, warning=FALSE}
library("tidyverse")
library("sf")
library("lwgeom")
library("mapboxapi")
library("leaflet")
library("reshape2")
library("geojsonio")
```

#### IMPORT NON-SPATIAL DATA

```{r, message=FALSE, warning=FALSE}
listings <- read_csv("toronto-listings.csv")
```

------------------------------------------------------------------------

### QUESTION 1 (5 marks)

What does the following block of code accomplish? Answer according to
the '\# Number' on each line.

```{r, message=FALSE, warning=FALSE}
listings$price <- substring(listings$price, 2, nchar(listings$price)-3) # 1
listings$price <- as.numeric(listings$price) # 2

listings <- listings %>% # 3
  mutate(bathrooms = as.numeric(str_split_fixed(listings$bathrooms_text, " b", 2)[,1])) %>% # 4
  filter(!is.na(room_type) & room_type == "Entire home/apt") # 5

```

**Written answer**:

1.  Changed data in price column to have only integer part by substring
    function
2.  Changed listings\$price from character type to numemric type
3.  Piping and applying the following functions to listings list
4.  Created bathroom column which has character before ' b' in numeric
    type
5.  Retrieve only columns that room_type is not NA or equals to 'Entire
    home/apt'

################################################## 

**DO NOT REMOVE \| FOR TEACHING ASSISTANTS ONLY** **GRADE/COMMENTS**

################################################## 

------------------------------------------------------------------------

### QUESTION 2 (3 marks)

What is the most frequent neighbourhood ("neighbourhood_cleansed") where
Airbnbs are located in Toronto and how many Airbnbs are within the
neighbourhood?

```{r}
neighbourhood_cleansed_df <- listings %>%
  group_by(neighbourhood_cleansed) %>%
  summarise(neighbourhood_cleansed_n = n()) %>%
  filter(neighbourhood_cleansed_n == max(neighbourhood_cleansed_n))

name_neighbourhood_cleansed <- as.character(neighbourhood_cleansed_df[,1])
count_neighbourhood_cleansed <- as.numeric(neighbourhood_cleansed_df[,2])
```

**Written answer**: The most frequent neighbourhood where Airbnbs are
located is **`r name_neighbourhood_cleansed `** with
**`r count_neighbourhood_cleansed`** Airbnbs.

################################################## 

**DO NOT REMOVE \| FOR TEACHING ASSISTANTS ONLY** **GRADE/COMMENTS**

################################################## 

------------------------------------------------------------------------

### QUESTION 3 (2 marks)

Some Airbnbs require you to rent the space for 2 or more nights. Create
a new variable (i.e., column) in the listings dataframe to represent the
minimum amount of money needed to rent the Airbnb. Name this variable
total_cost. Additionally, remove NA values from the total_cost column
(this will make things easier for you later).

```{r}
listings <- listings %>%
  filter(!(is.na(minimum_nights) | is.na(price))) %>%
  mutate(total_cost = price * minimum_nights)
```

################################################## 

**DO NOT REMOVE \| FOR TEACHING ASSISTANTS ONLY** **GRADE/COMMENTS**

################################################## 

------------------------------------------------------------------------

### QUESTION 4 (6 marks)

What is the average (mean) and the median total cost of Airbnbs in
Toronto with the following criteria (see below). Round your answers to
one decimal place within the in-line code.

1.  Minimum number of nights is equal to or less than 3
2.  Number of bathrooms is equal to two or more

```{r}
mean_med_total_cost <- listings %>%
  filter(minimum_nights <= 3 & bathrooms >= 2) %>%
  summarise(mean_total_cost= mean(total_cost),
            median_total_cost = median(total_cost)) %>%
  round(digits = 1)
mean_total_cost <- as.numeric(mean_med_total_cost[,1])
median_total_cost <- as.numeric(mean_med_total_cost[,2])
```

**Written answer**: The average cost of an Airbnb in Toronto with a
minimum of 3 or fewer nights is **`r mean_total_cost`** and the median
cost is **`r median_total_cost`**

################################################## 

**DO NOT REMOVE \| FOR TEACHING ASSISTANTS ONLY** **GRADE/COMMENTS**

################################################## 

------------------------------------------------------------------------

### QUESTION 5 (2 marks)

What does the mean and median tell us about the total cost of an Airbnb
in Toronto?

**Written answer**: The distribution of total cost of an Airbnb in
Toronto is right-skewed since mean is larger than median.

################################################## 

**DO NOT REMOVE \| FOR TEACHING ASSISTANTS ONLY** **GRADE/COMMENTS**

################################################## 

------------------------------------------------------------------------

### QUESTION 6 (4 marks)

Calculate the interquartile range of the total cost of Airbnbs that only
require 1 night. Either create a new dataframe, or environment variables
with the 25th and 75th percentile values. Make sure you can use the
values in the next question.

```{r}
iqr_total_cost <- listings %>%
  filter(minimum_nights == 1) %>%
  summarise(q1_total_cost = quantile(total_cost, 0.25),
            q3_total_cost = quantile(total_cost, 0.75)) %>%
  mutate(iqr_total_cost = q3_total_cost - q1_total_cost)

```

**Written answer**: The interquartile range of total cost for one-night
minimum Airbnbs in Toronto is **`r iqr_total_cost[1]` to
`r iqr_total_cost[2]`**.

################################################## 

**DO NOT REMOVE \| FOR TEACHING ASSISTANTS ONLY** **GRADE/COMMENTS**

################################################## 

------------------------------------------------------------------------

### QUESTION 7 (4 marks)

Create a boxplot with ggplot of the total cost of Airbnbs that only
require 1 night. Make sure to label the y-axis of your boxplot.

```{r}
listings %>%
  filter(minimum_nights == 1) %>%
  ggplot(aes(x = 0, y = total_cost)) +
  geom_boxplot() +
  ylab('Total Cost')
```

################################################## 

**DO NOT REMOVE \| FOR TEACHING ASSISTANTS ONLY** **GRADE/COMMENTS**

################################################## 

------------------------------------------------------------------------

### QUESTION 8 (3 marks)

What does the interquartile range and boxplot tell us about the total
cost of Airbnbs only requiring a one-night stay?

**Written answer**: The IQR is defined as the range of middle-half (50%)
of the total cost data is **`r iqr_total_cost[3]`**. 
The boxplot tells
that the data is extremely right-skewed.

################################################## 

**DO NOT REMOVE \| FOR TEACHING ASSISTANTS ONLY** **GRADE/COMMENTS**

################################################## 

------------------------------------------------------------------------

## PART 2: Spatial descriptive statistics

#### IMPORT DATA

```{r, message=FALSE, warning=FALSE}
# IMPORT AND CONVERT DATA
ls <- st_as_sf(listings, coords = c("longitude", "latitude"), crs = 4326) # Toronto Airbnb listings, ls = listings spatial
ls <- st_transform(ls, crs = 32617)

nbs <- st_read("toronto-neighbourhoods.geojson", crs = 4326) # Toronto neighbourhoods, nb = neighbourhoods
nbs <- st_transform(nbs, crs = 32617)
nbs_sp <- geojson_read("toronto-neighbourhoods.geojson", what = "sp") # Used for mapping

poi <- st_read("Places-of-Interest-and-Attractions.geojson") # Points of Interest in Toronto, poi = Points of Interest

poi_m <- st_transform(poi, crs = 32617) # poi_m = Points of Interest in meters

# CREATE LAT/LON COLUMNS
ls$coords <- as.character(ls$geometry)
ls$coords <- substring(ls$coords, 3, nchar(ls$coords)-1)
ls <- ls %>%
  mutate(longitude_m = as.numeric(str_split_fixed(ls$coords, ", ", 2)[,1]),
         latitude_m = as.numeric(str_split_fixed(ls$coords, ", ", 2)[,2]))

poi$coords <- as.character(poi$geometry)
poi$coords <- substring(poi$coords, 3, nchar(poi$coords)-1)
poi <- poi %>%
  mutate(longitude = as.numeric(str_split_fixed(poi$coords, ", ", 2)[,1]),
         latitude = as.numeric(str_split_fixed(poi$coords, ", ", 2)[,2]))

poi_m$coords <- as.character(poi_m$geometry)
poi_m$coords <- substring(poi_m$coords, 3, nchar(poi_m$coords)-1)
poi_m <- poi_m %>%
  mutate(longitude_m = as.numeric(str_split_fixed(poi_m$coords, ", ", 2)[,1]),
         latitude_m = as.numeric(str_split_fixed(poi_m$coords, ", ", 2)[,2]))


nbs$coords <- as.character(nbs$geometry)
nbs$coords <- substring(nbs$coords, 3, nchar(nbs$coords)-1)
nbs <- nbs %>%
  mutate(longitude = as.numeric(str_split_fixed(nbs$coords, ", ", 2)[,1]),
         latitude = as.numeric(str_split_fixed(nbs$coords, ", ", 2)[,2]))
```

------------------------------------------------------------------------

### QUESTION 9 (2 marks)

You and 4 friends would like to rent an Airbnb in Toronto for 5 nights
to spend some time in the city and visit Toronto's museums. You'd like
to pay no more than \$250/night (collectively), the Airbnb must have at
least 2 bathrooms, and the Airbnb must accommodate 5 or more people.
Create a new dataframe considering your criteria.

```{r}
criteria_ls <- listings %>%
  filter(minimum_nights <= 5 &
      price <= 250 &
      bathrooms >= 2 &
      accommodates >= 5)
```

################################################## 

**DO NOT REMOVE \| FOR TEACHING ASSISTANTS ONLY** **GRADE/COMMENTS**

################################################## 

------------------------------------------------------------------------

### QUESTION 10 (22 marks)

You and your 4 friends would also like to stay in a neighbourhood that
is in the middle of art gallery locations in the city, so you are
located centrally.

1.  Filter the Points of interest ('poi') dataframe to select only Art
    Galleries ('Gallery')
2.  Create 3 map icon/markers for the map. Be creative with your
    icon/marker image, but make sure it is representative and the
    resulting map is clear.
3.  Create the leaflet map with:

-   A basemap (your choice)

-   An appropriate zoom level

-   Map markers

    -   Airbnbs
    -   Art galleries with a popup with the gallery name
    -   Mean centre of art galleries
    -   Neighbourhoods with a popup with the neighbourhood name

4.  Identify the neighbourhood where the mean centre of art galleries is
    located.
5.  Identify the lowest cost Airbnb within the identified neighbourhood.
6.  Write a sentence identifying the following with inline code:

-   Cheapest cost Airbnb within neighbourhood
-   Cost of the Airbnb for a five-night stay
-   A clickable URL link ('listing_url') to the Airbnb you will stay

```{r}
# 1. FILTER THE POINTS OF INTEREST
poi <- poi %>%
  filter(CATEGORY == 'Gallery')
```

################################################## 

**DO NOT REMOVE \| FOR TEACHING ASSISTANTS ONLY** **GRADE/COMMENTS**

################################################## 

```{r}
# 2. CREATE POINT MARKERS TO MAP YOUR POINTS
# USE ANY MARKERS (i.e., PICTURES OFF THE INTERNET) YOU PLEASE, BUT MAKE SURE YOUR FINAL MAP IS LEGIBLE AND APPROPRIATE

# AIRBNBs
customPoint <- makeIcon(
  iconUrl = "https://cdn.discordapp.com/attachments/771483303093600316/864514198809870356/wfwef.png",
  iconWidth = 25, iconHeight = 25,
  iconAnchorX = 12.5, iconAnchorY = 12.5
)

# ART GALLERIES
artgallery_pts <- makeIcon(
  iconUrl = "https://commonculture.org.uk/wp-content/uploads/leaflet-maps-marker-icons/heritage.png",
  iconWidth = 30, iconHeight = 30,
  iconAnchorX = 15, iconAnchorY = 15
)


# MEAN CENTRE
mcIcon <- makeIcon(
  iconUrl = "https://media.discordapp.net/attachments/771483303093600316/864443508311851008/circle-cropped.png",
  iconWidth = 40, iconHeight = 40,
  iconAnchorX = 20, iconAnchorY = 20
)

```

################################################## 

**DO NOT REMOVE \| FOR TEACHING ASSISTANTS ONLY** **GRADE/COMMENTS**

################################################## 

```{r}
# 3. CREATE THE LEAFLET MAP
leaflet() %>%
  
  # ADD MAP LAYER, BASEMAPS http://leaflet-extras.github.io/leaflet-providers/preview/index.html MAKE SURE THEY DO NOT REQUIRE AN API TOKEN
  addProviderTiles(providers$CartoDB.DarkMatter) %>%
  
  # SET FIRST VIEW POINT (MAP CENTRE AND ZOOM LEVEL)
  setView(lng = mean(criteria_ls$longitude),
          lat = mean(criteria_ls$latitude),
          zoom = 11.7) %>%
  
  # AIRBNBs (HINT: Use the dataframe from Q9)
  addMarkers(lng = criteria_ls$longitude,
             lat = criteria_ls$latitude,
             icon = customPoint,
             popup = paste(sep="<br/>",
                           paste(criteria_ls$name),
                           paste('Total cost: $',
                                 paste('<b>',criteria_ls$total_cost,'</b>')))) %>%
  
  
  # ART GALLERIES
  addMarkers(lng = poi$longitude,
             lat = poi$latitude,
             icon = artgallery_pts,
             popup = paste(poi$NAME)) %>%
  
  # MEAN CENTRE
  addMarkers(lng = mean(poi$longitude),
             lat = mean(poi$latitude),
             icon = mcIcon,
             popup = paste('Mean Center')) %>%
  
  # ADD NEIGHBOURHOODS (HINT: USE 'nbs_sp')
  
  addPolygons(data = nbs_sp,
              color='aquamarine',
              popup = paste('Neighbourhood:', nbs_sp$neighbourhood))



```

################################################## 

**DO NOT REMOVE \| FOR TEACHING ASSISTANTS ONLY** **GRADE/COMMENTS**

################################################## 

```{r}
# PARTS 4, 5, AND 6
# HINT: CLICK THE NEIGHBOURHOOD FOR A POPUP WITH THE NAME OF THE NEIGHBOURHOOD


mc_poi_neighbourhood <- 'Bay Street Corridor'


lowest_airbnb <- criteria_ls %>%
  filter(neighbourhood_cleansed == mc_poi_neighbourhood) %>%
  filter(total_cost == min(total_cost)) %>%
  select(name, total_cost, listing_url)

name_lowest_airbnb <- as.character(lowest_airbnb[,1])
cost_lowest_airbnb <- as.numeric(lowest_airbnb[,2])
listing_url <- as.character(lowest_airbnb[,3])
```

**Written answer**: The cheapest cost Airbnb is named **`r name_lowest_airbnb`**
and it will cost **`r cost_lowest_airbnb`** dollars for the 5 night stay and the
[Airbnb can be seen here](`r listing_url`).

################################################## 

**DO NOT REMOVE \| FOR TEACHING ASSISTANTS ONLY** **GRADE/COMMENTS**

################################################## 

------------------------------------------------------------------------

### QUESTION 11 (3 marks)

Is a neighbourhood a good method to search for an Airbnb based on the
mean centre of Art Galleries? Why or why not?

**Written answer**: No, as the leaflet map example shown above, it was a case
that choosing a neighbourhood as a method for searching Airbnb becoming a
problem due to Segmentation of Areal Units. The mean center was located very
close to the borderline of one or two adjacent neighbourhood areas but 
realistically the calculation of minimum total cost of Airbnb is done within
the absolute boundary of the neighbourhood it locates.

################################################## 

**DO NOT REMOVE \| FOR TEACHING ASSISTANTS ONLY** **GRADE/COMMENTS**

################################################## 
